---
title: "Short-Term Management of Water-Damage Claim Risk Using Ensemble Precipitation Forecasts"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repository contains necessary code for reproducing results presented in the paper by Otneim et. al (2026). Since the insurance data is not publicly available, we have generated data from one of the models using the script *R/0_making_toydata.R*. This uses the estimated logistic regression model for Oslo and Bergen to generate a toy dataset. Thus, you will not be able to reproduce the specific results in the paper, but you have a running example with similar similar properties to the real data. 

The script *0_run_scripts.R* explains the order of how things should be run. The resulting predictions are stored the predictions folder and figures are stored in the figures folder. The script is included below. 

```{r}
#| eval: false
#| echo: true
# Run scripts
# Set up directories:
dir.create("predictions")
dir.create("figures")


# Generate toy data:
source("R/1_making_toydata.R")

# Fit models:
# -- Warning!!! require some time ---
source("R/2_models_fit.R")


# Run the CNN model in Python
#python/run_CNN.py

# Then add the prediction from the CNN
source("R/2b_add_CNN_predictions.R")

# Genenerate results figures: 
source("R/3_PRAUC_plots.R") # Takes a few minutes due to bootstrap
source("R/4_reliability.R")

```

## Precipitation data
The 51 ensemble forecasts and observed rain are stored in *data/forecast_data.rds*. The column *obs* is observed rain from the ERA5-reanalysis aggregated over the two cities (as described in the paper), while the columns '1'-'51' are the ordered ensemble forecasts from European Centre for Medium Range Weather Forecasts (Buizza et al., 2018) obtained from the MARS archive (European Centre for Medium-Range Weather Forecasts (ECMWF), 2024). 


## References

- Buizza, R., Alonso Balmaseda, M., Brown, A., English, S. J., Forbes, R., Geer, A., Haiden, T., Leutbecher, M., Magnusson, L., Rodwell, M., Sleigh, M., Stockdale, T., Vitart, F., and Wedi, N.: The Development and Evaluation Process Followed at ECMWF to Upgrade the Integrated Forecasting System (IFS), ECMWF Technical Memorandum 829, European Centre for Medium-Range Weather Forecasts (ECMWF), [https://doi.org/10.21957/xzopnhty9](https://doi.org/10.21957/xzopnhty9), 2018.
- European Centre for Medium-Range Weather Forecasts (ECMWF): Access to forecasts, [https://www.ecmwf.int/en/forecasts/accessing-forecasts](https://www.ecmwf.int/en/forecasts/accessing-forecasts), accessed: 2024-09-05, 2024.
- Hersbach, H., Bell, B., Berrisford, P., Biavati, G., Horányi, A., Muñoz Sabater, J., Nicolas, J., Peubey, C., Radu, R., Rozum, I., Schepers, D., Simmons, A., Soci, C., Dee, D., and Thépaut, J.-N.: ERA5 hourly data on single levels from 1940 to present, [https://doi.org/10.24381/cds.adbb2d47](https://doi.org/10.24381/cds.adbb2d47), [data set], 2023.
- Otneim, H., Dunn-Sigouin, E., Hølleland, S., Gorji, M., and Berentsen, G. D.: Short-Term Management of Water-Damage Claim Risk Using Ensemble Precipitation Forecasts, working paper, 2026.

